### 2014-09-06 eval.tex

{\bf Prototype Implementation}  In our prototype implementation of \tool, we used the Z3 SMT solver for constraint resolution \cite{DeMoura:2008}. For static analysis, to discover unexecuted branches, we utilize the SOOT compiler framework \cite{Vallee-Rai:1999}.

>>>>

{\bf Prototype Implementation}  In our prototype implementation of \tool, we used the Z3 SMT solver for constraint resolution \cite{MouraB08}. For static analysis, to discover unexecuted branches, we utilize the SOOT compiler framework \cite{Vallee-RaiCGHLS99}.

### 2014-09-06 guarantee.tex
changes

\begin{mytheorem}[Soundness]
The trace $\tau$ returned by our solver is a feasible trace for the concurrent program.
\end{mytheorem}

\begin{proof}
The proof consists of two parts: (1) the trace is feasible, and (2) the trace can be generated by the program. We sketch the proof as follows.
\begin{itemize}
\item  $\tau$ is feasible. Researchers~\cite{chao,maximal} point out a trace is feasible iff it satisfies the sequential consistency, i.e., $\forall object\ o, \tau\downarrow_{o}$ satisfies the serial specification of the object $o$. If  all the events considered are of the types in Table~\ref{Ta:syntax}, then the sequential consistency precisely means the following: (1) read-write consistency, i.e., each read event of a variable should contain the value written by the most recent write event, and (2) the synchronization consistency, e.g., the lock acquire and release of a lock should not be interleaved by the lock operations of the same lock, the begin event of a thread should follow the fork event of the parent thread. Our inter-thread data flow constraints guarantee the read-write consistency among shared locations. The SSA form encodes the read-write consistency among local variables. The synchronization consistency is also captured as constraints in our solver. 
\item $\tau$ can be generated by the program, i.e., for each thread $t$, $\tau\downarrow_{t}$ can be generated by the corresponding thread code.
This claim requires that,  for any two adjacent events $e$ and $e'$ in  $\tau\downarrow_{t}$, (1) if $e$ is not a branch, $inst^e$ and $inst^{e'}$ should be adjacent in the code; (2) if $e$ is a branch, $inst^e$ and $inst^{e'}$ should be adjacent and the $inst^e$ should be evaluated as the boolean value indicated by $inst^{e'}$. 
We derive the trace  through either concrete execution or symbolic execution, which satisfies the requirements and guarantees the correctness of the claim.
\end{itemize}
\end{proof}

\begin{mydiscussion}[Detection Capability]
Our technique has stronger detection capability than existing techniques~\cite{yannis,jeff,said}.
\end{mydiscussion}

@@

\begin{figure}[htp]
\centering
\includegraphics[scale=0.7]{figs/Visio-discuss.pdf}
\caption{Illustration of Detection Capability.}\label{fig:discuss}
\end{figure}

>>>>

\begin{mytheorem}[Soundness]
The trace computed by the solver,  $\tau'=<\Gamma , \{\tau_{t_1}, \tau_{t_2}, \dots \tau_{t_n} \}, O', \theta'>$, is a feasible trace for the concurrent program, where $O'$ defines its schedule and $\theta'$ defines the value mapping.
\end{mytheorem}

\begin{proof}
The proof consists of two parts: (1) the trace is feasible, and (2) the trace can be generated by the program. We sketch the proof as follows.
\begin{itemize}
\item  $\tau'$ is feasible. Researchers~\cite{chao,maximal} point out a trace is feasible iff it satisfies the sequential consistency, i.e., $\forall object\ o, \tau'\downarrow_{o}$ satisfies the serial specification of the object $o$. If  all the events considered are of the types in Table~\ref{Ta:syntax}, then the sequential consistency precisely means the following: (1) read-write consistency, i.e., each read event of a variable should contain the value written by the most recent write event, and (2) the synchronization consistency, e.g., the lock acquire and release of a lock should not be interleaved by the lock operations of the same lock, the begin event of a thread should follow the fork event of the parent thread. Our inter-thread data flow constraints guarantee the read-write consistency among shared locations. The SSA form encodes the read-write consistency among local variables. The synchronization consistency is also captured as constraints in our solver. 
\item $\tau$ can be generated by the program, i.e., for each thread $t$, $\tau'\downarrow_{t}$ can be generated by the corresponding thread code.
This claim requires that,  for any two adjacent events $e$ and $e'$ in  $\tau'\downarrow_{t}$, (1) if $e$ is not a branch, $inst^e$ and $inst^{e'}$ should be adjacent in the code; (2) if $e$ is a branch, $inst^e$ and $inst^{e'}$ should be adjacent and the $inst^e$ should be evaluated as the boolean value indicated by $inst^{e'}$. 
We derive the trace  through either concrete execution or symbolic execution, which satisfies the requirements and guarantees the correctness of the claim.
\end{itemize}
\end{proof}

\begin{mydiscussion}[Detection Capability]
Our technique has stronger detection capability than existing techniques~\cite{yannis,jeff, said}.
\end{mydiscussion}

@@

\begin{figure}[htp]
\centering
\includegraphics[width=4cm,height=4cm]{figs/Visio-discuss.pdf}
\caption{Illustration of Detection Capability.}\label{fig:discuss}
\end{figure}

### 2014-09-06 overview.tex

@@

For the racy events, $e_2$ and $e_7$, we first specify the race condition constraint  $\theta'(R^4_y)\leq 2\rightarrow O'_{e_2}=O'(e_7)$. Note that the race condition constraint associates the race with the branch condition that enables each event.  Also we encode other necessary constraints such as the intra-thread order constraints, $O'(e_4)<O'(e_5)\wedge O'(e_4)<O'(e_7)$. The inter-thread

{\bf Constraint Solving\ } The formuals from the different encoding steps are conjoined and sent to an off-the-shelf solver such as {\sf z3}.  The race under analysis is guaranteed to be real if the solver returns a solution, which includes the scheduling order and the values for the variables.

>>>>

The formuals from the different encoding steps are conjoined and sent to the off-the-shelf solver such as {\sf z3}.  The race under analysis is real if the solver returns a solution, which includes the scheduling order and the values for the variables.

@@

For the racy events, $e_2$ and $e_7$, we first specify the race condition constraint  $\theta'(R^4_y)\leq 2\rightarrow O'_{e_2}=O'(e_7)$. Note that the race condition constraint associates the race with the branch condition that enables each event.  Also we need to encode (1) the intra-thread constraints, such as the  order constraints $O'(e_4)<O'(e_5)\wedge O'(e_4)<O'(e_7)$, and (2) the inter-thread constraints, which remain the same as before. With these constraints, the solver confirms the race pair, ($e_2$, $e_7$). More details are explained in Section~\ref{sec:relax2}.
